### 2018-06-29 Thesis/Parts/Data/Data.tex
Feedback update

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Corpus}
The dataset we used for this research consists of articles published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications. This results in a total dataset of $1.391.543$ articles from $3.759$ journals. Details about the corpus can be found in table~\ref{table:corpusSize}.
\begin{table}[hbt]
\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
 & Total count & Unique count & Average length \\
\hline\hline
Title words & $18.822.399$ & $939.665$ & 13,53  \\
\hline
Title tokens & $14.742.192$ & $230.805$ & 10,64 \\
\hline\hline
Abstract words & $264.653.020$ & $5.853.077$  & 190,19  \\
\hline
Abstract tokens & $171.474.473$ & $738.961$ & 123,71 \\
\hline\hline
Total words & $283.475.419$ & $6.209.769$  & 203,71 \\
\hline
Total tokens & $186.962.354$ & $763.475$ & 134,36 \\
\hline
\end{tabular}
\end{center}
\caption{Corpus size}\label{table:corpusSize}
\end{table}\\
The word occurrences follow the pattern of a pareto distribution as described by~\citet{wiegand2018word}. This distribution is visualized in figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/word_occurrences}
\caption{Word and token occurrences}\label{figure:wordTokenOccurrence}
\end{figure}

\header{Datasets}
For this researched we used a (pre-made) tokenized dataset, which reduces the total amount of words by 34\%, from this tokenized set, we created the embeddings and the TF-IDF feature vectors.
\subheader{Tokenization}
The following steps have been applied to the words to create a tokenized set:
\begin{enumerate}
\item{Removed punctuation}
\item{Removed all non-ASCII characters}
\item{Transformed all characters to lower-case}
\item{Removed stop-words, as provided by the NLTK library}
\item{Removed numbers}
\item{Stemmed all words, using the stemmer provided by the NLTK library}
\end{enumerate}
These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.

\subheader{Embedding}
For this research, we reused the word embeddings created by \citet{Truong2017Thesis}. These embeddings have a vector size of 300, which is an industry default. They have been trained on the entire Elsevier corpus, not limited to the subset we used for this research. To create article embeddings, we take the average of all normalized word embeddings for that article. Journal embeddings are created in the same way. We averaged all the normalized article embeddings to create the journal embeddings. We have used multiple embedding configurations for this research
\subsubheader{Default embedding}
The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set.
\subsubheader{TF-IDF embedding}
The TF-IDF weighted embedding set, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
The TF-IDF is calculated with a raw token count, and a smoothed inverted document frequency, calculated as follows:\\
\begin{equation}
IDF = \log_{10}(\dfrac{|A|}{|A_t|})
\end{equation}
Where $|A|$ is the total count of articles and $|A_t|$ is the count of articles containing term t.
The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
\subsubheader{10K TF-IDF embedding}
The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the number of tokens it uses. This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance.
\subsubheader{5K TF-IDF embedding}
The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise.
\subsubheader{1K-6K TF-IDF embedding}
The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words. The rationale for this is that common words will occur in many articles, creating noise, by cutting off the top 1.000 and cutting off everything below 6.000 we tried to reduce the noise by filtering common words. This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.

\subheader{TF-IDF}
To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from PySparks MlLib library. The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size. These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equal the number of hash buckets. To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
We denote the TF-IDF configurations as follows: $vocabulary size/hash bucket number$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.
\begin{figure}
\includegraphics[width=6in]{Plots/tfidf_selection_plot}
\caption{TF-IDF performance and memory usage}\label{figure:tfidfPerformance}
\end{figure}
\FloatBarrier
Figure~\ref{figure:tfidfPerformance} shows the performance, as median rank, and storage size, in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. The TF-IDF features are created on article level. We average the set of article embeddings to create a journal embedding.

@@

\subheader{Create training and validation set}
We split our initial set  $80\%$ - $20\%$. We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations. This split is based on a random number given to article each record, ensuring that all set have the same (random) training and validation set.
\subheader{Create journal embeddings}
From our training set we create the journal embeddings, which are created for most sets\footnote{see paragraph datasets} by averaging the article embeddings or feature vectors.
\subheader{Categorize validation articles}
To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal, during this process we keep track of:
\begin{itemize}
\item{Title-based-rank of the actual journal}
\item{Abstract-based-rank of the actual journal}
\item{Best scored journal on the abstract similarity}
\item{Best scored journal on the title similarity}
\item{Abstract similarity between the actual journal and the article}
\item{Title similarity between the actual journal and the article}
\end{itemize}
\subsubheader{Distance metrics}
To calculate the distance between to vectors, cosine similarity is commonly used. We validated the quality of cosine similarity as a distance metrics by comparing it to all other similarity matrices available in the SciPy library, which we used to calculate the distances. We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set. Table~\ref{table:distanceMetrics} shows the results of this validation.\\
\begin{table}[hbt]
\begin{tabular}{|l|l|l|l|l|}
\hline
Metric\footnote{As defined and provided by the SciPy library} & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\
\hline
Braycurtis & 28 & 130 & 23 & 124  \\
\hline
Canberra & 33 & 148 & 26 & 133  \\
\hline
Chebyshev & 57 & 256 & 41 & 191  \\
\hline
\textit{Cityblock} & \textit{28} & \textit{130} & \textit{23} & \textit{124}  \\
\hline
\textit{Correlation} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
\textbf{Cosine} & \textbf{27} & \textbf{127} & \textbf{23} & \textbf{122}  \\
\hline
Dice & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Euclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Hamming & 1995 & 1929 & 1995 & 1929  \\
\hline
Jaccard & 1995 & 1929 & 1995 & 1929  \\
\hline
Kulsinski & 1995 & 1929 & 1995 & 1929  \\
\hline
Mahalanobis & 136 & 544 & 75 & 449  \\
\hline
Matching & 1995 & 1929 & 1995 & 1929  \\
\hline
Rogerstanimoto & 1995 & 1929 & 1995 & 1929  \\
\hline
Russellrao & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Seuclidean} & \textit{27} & \textit{124} & \textit{22} & \textit{115}  \\
\hline
Sokalmichener & 1995 & 1929 & 1995 & 1929  \\
\hline
Sokalsneath & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Sqeuclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Yule & 1995 & 1929 & 1995 & 1929  \\
\hline
\end{tabular}
\caption{Distance metric performance for word embeddings on the categorization of academic texts}\label{table:distanceMetrics}
\end{table}
These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& Sqeuclidean). This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets. The results show that some enhancement on the euclidean algorithm result in slightly improved results, although not significant. Also the Cityblock metric yields results close to the Cosine metric, it has a slightly worse performance, which is also not significant. Because of this, we will use the cosine-similarity as the distance matrix, which will make our results better comparable with other work.

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Corpus}
The dataset we used for this research consists of articles published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications. This results in a total dataset of $1.391.543$ articles from $3.759$ journals. Details about the corpus can be found in table~\ref{table:corpusSize}.
\begin{table}[hbt]
\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
 & Total count & Unique count & Average length \\
\hline\hline
Title words & $18.822.399$ & $939.665$ & 13,53  \\
\hline
Title tokens & $14.742.192$ & $230.805$ & 10,64 \\
\hline\hline
Abstract words & $264.653.020$ & $5.853.077$  & 190,19  \\
\hline
Abstract tokens & $171.474.473$ & $738.961$ & 123,71 \\
\hline\hline
Total words & $283.475.419$ & $6.209.769$  & 203,71 \\
\hline
Total tokens & $186.962.354$ & $763.475$ & 134,36 \\
\hline
\end{tabular}
\end{center}
\caption{Corpus size}\label{table:corpusSize}
\end{table}\\
\subheader{Text properties}
\citet{wiegand2018word} state that the Pareto distribution offers a good fit to the word occurrences in natural language. Their models show that, due to the additional parameters in the Pareto-III, the tail of the data fits better with the model than the Zipf model. This shows the relation between the word occurrences rank and the actual occurrences. This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare and scientific texts and novels\cite{thurner2015understanding}.
The word occurrences in our corpus also follow the pattern of a Pareto distribution as described by~\citet{wiegand2018word}. Our distribution is visualized in figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/word_occurrences}
\caption{Word and token occurrences}\label{figure:wordTokenOccurrence}
\end{figure}

\header{Datasets}
For this researched we used a (pre-made) tokenized dataset, created from the earlier described corpus, which reduces the total amount of words by 34\% (see table~\ref{table:corpusSize}). From this tokenized set, we created the embeddings and the TF-IDF feature vectors.
\subheader{Tokenization}
The following steps have been applied to the words to create a tokenized set:
\begin{enumerate}
\item{Removed punctuation}
\item{Removed all non-ASCII characters}
\item{Transformed all characters to lower-case}
\item{Removed stop-words, as provided by the NLTK\footnote{Natural Language ToolKit, \url{https://www.nltk.org/}} library}
\item{Removed numbers}
\item{Stemmed all words, using the stemmer provided by the NLTK library}
\end{enumerate}
These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.

\subheader{Embedding}
For this research, we reused the word embeddings created by \citet{Truong2017Thesis}. These embeddings have a vector dimension of 300, which is an industry default. They have been trained on the entire Elsevier corpus, not limited to the subset we used for this research. To create higher-level embeddings, we average all component embeddings. Thus, to create article embeddings, we take the average of all normalized word embeddings for that article. Journal embeddings are created by taking the average of all normalized article embeddings. We use the average to combine multiple embeddings into one, because we determine the meaning of a larger text as the average meaning of all components. Since this meaning is represented as an embedding, we can average the embeddings to create the "average meaning". We have used multiple embedding optimizations for this research.
\subsubheader{Default embedding}
The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the figures as "embedding".
\subsubheader{TF-IDF weighted embedding}
The TF-IDF weighted embedding set, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
The TF-IDF is calculated with a raw token count, and a smoothed inverted document frequency, calculated as follows:\\
\begin{equation}
IDF = \log_{10}(\dfrac{|A|}{|A_t|})
\end{equation}
Where $|A|$ is the total count of articles and $|A_t|$ is the count of articles containing term t.
The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word. We will refer to this embedding in the figures as "tfidf\_embedding".
\subsubheader{10K TF-IDF embedding}
The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the number of tokens it uses. This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance. We will refer to this embedding in the figures as the "10k\_embedding".
\subsubheader{5K TF-IDF embedding}
The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise. We will refer to this embedding in the figures as "5k\_embedding".
\subsubheader{1K-6K TF-IDF embedding}
The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words. The rationale for this is that common words will occur in many articles, creating noise, by cutting off the top 1.000 and cutting off everything below 6.000 we tried to reduce the noise by filtering common words. This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set. We will refer to this embedding in the figures as "1k\_6k\_embedding". We refer to the "10k\_embedding", "5k\_embedding" and the "1k\_6k\_embedding" as the limited TF-IDF embeddings, because these embedding use TF-IDF weighing, and have been limited in their vocabulary due to the cut-off's.
\subheader{TF-IDF}
To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from PySparks MlLib library. The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size. These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equal the number of hash buckets. To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
We label the TF-IDF configurations as follows: $vocabulary size/hash bucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation. This means that the set with a 10.000 vocabulary size and a 10.000 hash bucket size will be denoted as "10K/10K". We will refer to the TF-IDF configurations in our figures as "tfidf\_vocabulary size\_hash bucket size".
\begin{figure}[hbt]
\includegraphics[width=5in]{Plots/tfidf_selection_plot_performance}
\caption{TF-IDF performance on title and abstract}\label{figure:tfidfPerformance}
\end{figure}
\begin{figure}[hbt]
\includegraphics[width=5in]{Plots/tfidf_selection_plot_memory}
\caption{TF-IDF performance on title and abstract}\label{figure:tfidfMemory}
\end{figure}
\FloatBarrier
Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. The TF-IDF features are created on article level. We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings.

\header{Research environment}
The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data. \citet{armbrust2015spark} state that Spark SQL lets programmers leverage the benefits of relational processing and lets SQL users call complex analytic libraries in Spark. This allows for much tighter integration between relational and procedural processing. The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.

@@

\subheader{Create training and validation set}
We split our initial set  $80\%$ - $20\%$. We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations. This split is based on a random number given to article each record, ensuring that all set have the same (random) training and validation set.
\subheader{Create journal embeddings}
From our training set we create the journal embeddings, which are created for most sets\footnote{see paragraph datasets} by averaging the article embeddings or feature vectors.
\subheader{Categorize validation articles}
To categorize the articles, we calculate the distance between the title of the article, and the title of each journal from the validation set. We also do this for the abstract of the article and the abstract of each journal. During this process we keep track of:
\begin{itemize}
\item{Title-based-rank of the actual journal}
\item{Abstract-based-rank of the actual journal}
\item{Best scored journal on the abstract similarity}
\item{Best scored journal on the title similarity}
\item{Abstract similarity between the actual journal and the article}
\item{Title similarity between the actual journal and the article}
\end{itemize}
\subsubheader{Distance metrics}
To calculate the distance between to vectors, cosine similarity is commonly used. We validated the quality of cosine similarity as a distance metrics by comparing it to all other similarity matrices available in the SciPy library, which we used to calculate the distances. We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set. Table~\ref{table:distanceMetrics} shows the results of this validation.\\
\begin{table}[hbt]
\begin{tabular}{|l|l|l|l|l|}
\hline
Metric\footnote{As defined and provided by the SciPy library} & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\
\hline
Braycurtis & 28 & 130 & 23 & 124  \\
\hline
Canberra & 33 & 148 & 26 & 133  \\
\hline
Chebyshev & 57 & 256 & 41 & 191  \\
\hline
\textit{Cityblock} & \textit{28} & \textit{130} & \textit{23} & \textit{124}  \\
\hline
\textit{Correlation} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
\textbf{Cosine} & \textbf{27} & \textbf{127} & \textbf{23} & \textbf{122}  \\
\hline
Dice & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Euclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Hamming & 1995 & 1929 & 1995 & 1929  \\
\hline
Jaccard & 1995 & 1929 & 1995 & 1929  \\
\hline
Kulsinski & 1995 & 1929 & 1995 & 1929  \\
\hline
Mahalanobis & 136 & 544 & 75 & 449  \\
\hline
Matching & 1995 & 1929 & 1995 & 1929  \\
\hline
Rogerstanimoto & 1995 & 1929 & 1995 & 1929  \\
\hline
Russellrao & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Seuclidean} & \textit{27} & \textit{124} & \textit{22} & \textit{115}  \\
\hline
Sokalmichener & 1995 & 1929 & 1995 & 1929  \\
\hline
Sokalsneath & 1995 & 1929 & 1995 & 1929  \\
\hline
\textit{Sqeuclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
\hline
Yule & 1995 & 1929 & 1995 & 1929  \\
\hline
\end{tabular}
\caption{Distance metric performance for word embeddings on the categorization of academic texts}\label{table:distanceMetrics}
\end{table}
These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& Sqeuclidean). This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets. The results show that some enhancement on the euclidean algorithm result in slightly improved results, although not significant. Also the Cityblock metric yields results close to the Cosine metric, it has a slightly worse performance, which is also not significant. Because of this, we will use the cosine-similarity as the distance metric, which will make our results better comparable with other work.

### 2018-06-29 Thesis/Parts/Discussion/Discussion.tex
Feedback update

\documentclass[../../Thesis.tex]{subfiles}
\externaldocument{../Research_results/Research_results}
\externaldocument{../Data/Data}
\begin{document}
\header{Discussion}
\subheader{Result analysis}
\begin{jumpin}
\subsubheader{Best performers}
The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles. For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement compared to the default embeddings, which 1 median rank higher on the abstracts, and equal on the titles.

@@

\subsubheader{Limited TF-IDF embeddings}
The limited TF-IDF embeddings all underperform, compared to the non-limited TF-IDF embedding, on the median and average ranking. Indicating that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase or none at all. However, the rank lowers, indicating the reduction in embedding quality due to missing words. This is in line with what we found with the TF-IDF results; higher vocabulary sizes give better performance. However, figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings. Their pattern shows a decent performance indicates the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance. Indicating a better performance on the top-1 articles compared to the other sets.\\This leads us to believe that the cut-off was effective, but that it did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings. Resulting in high median and average ranks, and in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However, they can be processed more efficiently during calculations}. This results in a lower memory requirement.

\subsubheader{TF-IDF \& embeddings}
Our hypothesis on the difference between the TF-IDF and the standard embedding is as follows:\\
The embeddings seem to outperform the TF-IDF in situations when there is little information available, the titles in our case. This indicates that the embeddings store some word meaning that enables them to perform relatively well on the titles. The abstracts, on the other hand, contain much more information. Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information. 
If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, since the TF-IDF lacks the information to perform well. This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a major one. We would also expect on the abstract an increase in performance since the TF-IDF has more information in this context. We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance. Our data shows a minor improvement in performance of 1 median rank and 10 average ranks while these improvements cannot be seen as significant, our data at least indicates that weighting the embeddings with TF-IDF values has a positive effect on the embeddings.

\subsubheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding. The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (as displayed in figure~\ref{figure:tfidfPerformance}). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is significantly worse than the embedding, which also uses less memory.

@@

This research shows that even tough the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings. Earlier research already proposed improvements to the word embeddings. \citet{dai2015document} show that the usage of paragraph vectors improve the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative. While this looks promising, we have to keep in mind that our task differs from earlier tasks. We do not categorize on two categories but more than 3k. Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale., which complicates the task due to the "grey areas"  between categories, which increases given more categories. \citet{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task. \citet{wang2016linked} introduced the Linked Document Embedding method (LDE) method, which makes use of additional information about a document, such as citations. Their research specifically focused on categorizing documents, showed a 5.89\% increase of the micro-F1 score on LDE compared to CBOW, and a 9.11\% increase of the macro-F1 score. We would expect that applying this technique to our dataset would improve our scores, given earlier results on comparable tasks.\\

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\externaldocument{../Research_results/Research_results}
\externaldocument{../Data/Data}
\begin{document}
\header{Discussion}
\subheader{Result analysis}
\begin{jumpin}
\subsubheader{Best performers}
The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles. For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings, which 1 median rank higher on the abstracts, and equal on the titles.

@@

\subsubheader{Limited TF-IDF embeddings}
The limited TF-IDF embeddings all underperform, compared to the TF-IDF embedding (which does not have a limited vocabulary), on the median and average ranking. Indicating that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase or none at all. However, the rank lowers, indicating the reduction in embedding quality due to missing words. This is in line with what we found with the TF-IDF results; higher vocabulary sizes give better performance. However, figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings. Their pattern shows a decent performance indicates the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance. Indicating a better performance on the top-1 articles compared to the other sets.\\This seems to indicate that the cut-off was effective, but that it did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings. Resulting in high median and average ranks, and in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However, they can be processed more efficiently during calculations}. This results in a lower memory requirement.

\subsubheader{TF-IDF \& embeddings}
Our hypothesis on the difference between the TF-IDF and the standard embedding is as follows:\\
The embeddings seem to outperform the TF-IDF in situations when there is little information available, the titles in our case. This indicates that the embeddings store some word meaning that enables them to perform relatively well on the titles. The abstracts, on the other hand, contain much more information. Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information. 
If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, since the TF-IDF lacks the information to perform well. This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a significant one. We would also expect on the abstract an increase in performance since the TF-IDF has more information in this context. We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance. Our data shows a minor improvement in performance of 1 median rank and 10 average ranks while these improvements cannot be seen as significant, our data at least indicates that weighting the embeddings with TF-IDF values has a positive effect on the embeddings.

\subsubheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding. The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (as displayed in figure~\ref{figure:tfidfPerformance}). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is significantly worse than the embedding, which also uses less memory. This indicates that the embeddings are able to store the relatedness information more densely than the TF-IDF feature vectors can store the worod occurrence information.

@@

This research shows that even tough the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings on the abstracts. Earlier research already proposed improvements to the word embeddings. \citet{dai2015document} show that the usage of paragraph vectors improve the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative. While this looks promising, we have to keep in mind that our task differs from earlier tasks. We do not categorize on two categories but more than 3k. Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale, which complicates the task due to the "grey areas"  between categories. These are the area's in which the classification algorithm is "in doubt" and could reasonably assing the article to both journals. The number of these grey areas increases given more categories. \citet{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task. \citet{wang2016linked} introduced the Linked Document Embedding method (LDE) method, which makes use of additional information about a document, such as citations. Their research specifically focused on categorizing documents, showed a 5.89\% increase of the micro-F1 score on LDE compared to CBOW, and a 9.11\% increase of the macro-F1 score. We would expect that applying this technique to our dataset would improve our scores, given earlier results on comparable tasks.\\

### 2018-06-29 Thesis/Parts/Future_work/Future_work.tex
Feedback update

\subheader{Method differences}
\citet{levy2015improving} observed that there were no significant differences between the various embedding creation methods. They state that the global/hyperparameters mainly cause the difference in performance. In this research, we have not looked at the comparison between various models and (hyper) parameters. We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best possible performance. Future work could seek to validate the results of \citet{levy2015improving} by expanding our research with multiple metrics. It should be noted however that Levy et al. base their conclusions on word similarity and word analogy tasks, and not on categorization. This is the reason why we did not take this research into account in our discussion since their experiments are not comparable to ours.

\subheader{Intelligent cutting}
An interesting improvement to enhance the word embeddings with could be a smarter way to remove noise, based on word embeddings. This might be achieved by analyzing the word embedding spectrum before normalization, and to then cut the center of the vector space out. This must be applied before normalization since normalization causes all embeddings to have a distance of 1 to the center point. All words which are generic are in the center of the spectrum. Removing these words prevents the larger texts to be pulled towards the middle, where they lose the parts of their meaning which sets them apart from the other journals. We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.

>>>>

\subheader{Method differences}
\citet{levy2015improving} observed that there were no significant differences between the various embedding creation methods. They state that the global/hyperparameters of the various methods mainly cause the difference in performance. In this research, we have not looked at the comparison between various models and (hyper) parameters. We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best possible performance. Future work could seek to validate the results of \citet{levy2015improving} by expanding our research with multiple metrics. It should be noted however that Levy et al. base their conclusions on word similarity and word analogy tasks, and not on categorization. This is the reason why we did not take this research into account in our discussion since their experiments are not comparable to ours.

\subheader{Intelligent cutting}
An interesting improvement to enhance the word embeddings with could be a smarter way to remove noise, based on word embeddings. This might be achieved by analyzing the word embedding spectrum before normalization, and to then cut the center of the vector space out. This must be applied before normalization since normalization causes all embeddings to have a distance of 1 to the center point. All words which are generic are in the center of the spectrum. Removing these words prevents the larger texts to be pulled towards the middle of the vector space, where they lose the parts of their meaning which sets them apart from the other journals. We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.
